---
title: "Homework 5"
author: "Yuan Meng"
date: 2021-11-16
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

Problem 1
```{r}
homicidie_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>%
  mutate(
    city_state = str_c(city,state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")

```

Baltimore MD

```{r}
baltimore_df = 
  homicidie_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )
baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n))

baltimore_test  %>%
  broom::tidy()
```

```{r}
prop_test_function = function(city_df){

  city_summary = 
  city_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )
  
  city_test = 
  prop.test(
    x = city_summary %>% pull(unsolved),
    n = city_summary %>% pull(n))
  
  return(city_test)
}


prop_test_function(baltimore_df)

homicidie_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

```{r}
result_df = 
  homicidie_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results)

result_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Problem 2
```{r message=FALSE}
study_df = 
  tibble(
    files = list.files("./data/zip_data")) %>%
  mutate(
    files_id = str_remove(files, ".csv"),
    files = str_c("./data/zip_data/", files),
    data = map(files, read_csv)
        ) %>%
    separate(files_id, into = c("treatment_arm", "id"), sep = "_") %>% 
    mutate(
      treatment_arm = case_when(
      treatment_arm == "con" ~"control",
      treatment_arm == "exp" ~ "experimental")) %>%  # divide control and experimental arm
    select(-files) %>%
    relocate(id) %>%
    unnest(data) 

knitr::kable(study_df)

```

```{r}
clean_df = 
  study_df %>%
    pivot_longer(
        week_1:week_8,
        names_to = "week",
        names_prefix = "week_",
        values_to = "observation") %>%
    mutate(
      week = as.numeric(week)
      ) 
clean_df
```

This is the tidy data after cleaning. We have `r nrow(clean_df)` participants. The data contain subject ID, arm, and observations over time.

```{r}
clean_df %>%
  ggplot(aes(x = week, y = observation, group = id )) +
  geom_line(aes(color = id)) +
  facet_grid(. ~ treatment_arm)
```

The experimental group have increasing observations over time. Compare to experimental group, control are more stable. The observation of control group lower than experimental group overall. There are more divergence occur after week 2 and 3. 

Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names() 
```

Write function

```{r}
fill_in_missing = function(vector){
  if (is.numeric(vector)){
    mean_value = mean(vector, na.rm = TRUE)
    vector = replace_na(vector, mean_value)
  }
  else if(is.character(vector)){
    vector = replace_na(vector, "virginica")
  }
}

filled_iris = 
  map(iris_with_missing, fill_in_missing) %>% 
  as_tibble() 

filled_iris
table(is.na(filled_iris)) # use this function to show there is no NA in the table 
```

